Step1_LoadData

### 2024-07-31 ProxySelection.Rmd
saved workspace
Add estimated RD & the SE.
Updated / added code chunks: Chunk 4 (bross RD), Chunk 6 (hybrid RD), Chunk 9 (lasso RD), Chunk 11 (enet ED), Chunk 13 (xgb RD), Chunk 15 (ga RD), Chunk 18 (svm RD), Chunk 20 (Boruta RD), Chunk 22 (fs RD), Chunk 24 (bs RD), Chunk 26 (sw RD), Chunk 28 (rf OR-cont), Chunk 29 (rf RD), Chunk 39 (OR.ci_plot with # of proxy), Chunk 40 (summary RD all methods), Chunk 41 (print RD result table), chunk 42 (print OR.ci_plot with # of proxy)

**Method 1: Bross Formula**
```{r bross, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
out3 <- get_prioritised_covariates(df = out2,
                                   patientIdVarname = "idx", 
                                   exposureVector = basetable$exposure,
                                   outcomeVector = basetable$outcome,
                                   patientIdVector = patientIds, 
                                   k = 100)
hdps.dim <- out3$autoselected_covariate_df

@@

**Method 2: Hybrid Bross Formula & Lasso**
```{r hybrid, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()
proxy.list <- names(out3$autoselected_covariate_df[,-1])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit<-glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 1, 
                             nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.hybrid <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.hybrid)
fs.hybrid <- proxy.list.sel.hybrid

@@

@@

proxy.list <- names(out2[,-1])    # length(proxy.list) :  142
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )

```

**Method 3: Pure Lasso**
```{r lasso, warning=FALSE, cache=TRUE}
set.seed(42) # different seed -> different length for the selected proxy list
start_time <- Sys.time()
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                               x = covar.mat, 
                               type.measure='mse',
                               family="binomial",
                               alpha = 1, 
                               nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.ml <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.ml)
fs.lasso <- proxy.list.sel.ml
proxy.lasso <- paste0(fs.lasso, collapse = "+")
form.lasso <- paste0(c(covform, proxy.lasso), collapse = "+")
formula.lasso <- as.formula(paste0("exposure", "~", form.lasso))

@@

**Method 4: Elastic Net**
```{r enet, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
elas.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 0.5, 
                             nfolds = 5)
coef.fit<-coef(elas.fit, s='lambda.min', exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.elastic <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.elastic)
fs.elastic <- proxy.list.sel.elastic

@@

**Method 5: XGBoost**
```{r xgb, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
                    max.depth = 20, eta = 1, nthread = 2, nrounds = 5, 
                    objective = "binary:logistic")

@@

@@

_GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
```{r ga, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
gaOpt <- function(vars, IV.train, DV.train) {
	varNames <- colnames(IV.train) #getting names of all variables
	selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
	gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars

@@

@@

_(Long Running Time)_
```{r svm, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
svmTrainOutcome <- hdps.data$outcome
svmTrainOutcome[svmTrainOutcome == 0] <- -1
svmTrainPreds <- data.frame(covar.mat)

@@

```{r, warning=FALSE, cache=TRUE}
fs.svm <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
fs.svm <- proxy.list[proxy.list %in% fs.svm]
proxy.svm <- paste0(fs.svm, collapse = "+")
form.svm <- paste0(c(covform, proxy.svm), collapse = "+")
formula.svm <- as.formula(paste0("exposure", "~", form.svm))

@@

@@

_(Long Running Time)_
```{r Boruta, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()
boruta_output <- Boruta(Y.form, data = hdps.data, doTrace = 1)
sel.variables.bor <- names(boruta_output$finalDecision)[which(boruta_output$finalDecision != "Rejected")]
fs.boruta <- proxy.list[proxy.list %in% sel.variables.bor]
proxy.boruta <- paste0(fs.boruta, collapse = "+")
form.boruta <- paste0(c(covform, proxy.boruta), collapse = "+")
formula.boruta <- as.formula(paste0("exposure", "~", form.boruta))

@@

**Method 9.1: Stepwise Regression (Forward)**
```{r fs, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()
initial_formula <- as.formula(paste0("outcome~exposure+",
                                     covform,
                                     collapse = "+"))
full_formula <- as.formula(paste0("outcome~exposure+",
                                  rhsformula,
                                  collapse = "+"))

@@

**Method 9.2: Stepwise Regression (Backward)**
```{r bs, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
stepwise_backward <- stepAIC(full_model, direction = "backward")
fs.backward <- all.vars(formula(stepwise_backward))[-1]
fs.backward <- proxy.list[proxy.list %in% fs.backward]
fs.backward <- fs.backward[fs.backward != "exposure"]
proxy.backward <- paste0(fs.backward, collapse = "+")
form.backward <- paste0(c(covform, proxy.backward), collapse = "+")
formula.backward <- as.formula(paste0("exposure", "~", form.backward))

@@

**Method 9.3: Stepwise Regression (Both)**
```{r sw, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
stepwise_both <- stepAIC(initial_model, 
                            scope = list(lower = initial_model, 
                                         upper = full_model), 
                            direction = "both")
fs.both <- all.vars(formula(stepwise_both))[-1]
fs.both <- proxy.list[proxy.list %in% fs.both]
proxy.both <- paste0(fs.both, collapse = "+")
form.both <- paste0(c(covform, proxy.both), collapse = "+")
formula.both <- as.formula(paste0("exposure", "~", form.both))

@@

Comparing the Results:
```{r compare, warning=FALSE, cache=TRUE}
sum_ci.all <- rbind(sum_ci.bross, sum_ci.hybrid, sum_ci.lasso, sum_ci.elastic, 
                    sum_ci.xgboost, sum_ci.GA, sum_ci.svm, sum_ci.boruta,
                    sum_ci.forward, sum_ci.backward, sum_ci.both)

OR.data <- data.frame(method = c("bross", "hybrid", "lasso", "elastic", 
                                 "xgboost", "GA", "SVM", "boruta", 
                                 "forward", "backward", "both"),
                      OR = exp(sum_ci.all[,2]),
                      lower = exp(sum_ci.all[,5]),
                      upper = exp(sum_ci.all[,6]))

OR.data$method <- factor(OR.data$method, 
                         levels = c("both", "backward", "forward",
                                    "boruta", "SVM", "GA", "xgboost", 
                                    "elastic", "lasso", "hybrid", "bross"))

fs.all <- data.frame(numFeature = c(length(fs.bross), 
                                    length(fs.hybrid),
                                    length(fs.lasso), 
                                    length(fs.elastic), 
                                    length(fs.xgboost),
                                    length(fs.GA),
                                    length(fs.svm),
                                    length(fs.boruta),
                                    length(fs.forward),
                                    length(fs.backward),
                                    length(fs.both)),
                     numInCommon = c(NA,
                                     length(fs.hybrid[fs.hybrid %in% fs.bross]),
                                     length(fs.lasso[fs.lasso %in% fs.bross]),
                                     length(fs.elastic[fs.elastic %in% fs.bross]),
                                     length(fs.xgboost[fs.xgboost %in% fs.bross]),
                                     length(fs.GA[fs.GA %in% fs.bross]),
                                     length(fs.svm[fs.svm %in% fs.bross]),
                                     length(fs.boruta[fs.boruta %in% fs.bross]),
                                     length(fs.forward[fs.forward %in% fs.bross]),
                                     length(fs.backward[fs.backward %in% fs.bross]),
                                     length(fs.both[fs.both %in% fs.bross])))
rownames(fs.all) <-  c("bross", "hybrid", "lasso", "elastic", 
                       "xgb", "GA", "SVM", "boruta",
                       "forward", "backward", "both")

fs.commonOneToOne <- data.frame(ini = rep(NA, 11))

for (i in 1:11) {
  col_name <- OR.data$method[i]
  if (col_name == "SVM") {
    col_name <- "svm"
  }
  na.i <- 1
  na <- c()
  while (na.i < i) {
    na <- c(na, NA)
    na.i <- na.i + 1
  }
  num_common <- c(length(fs.bross[fs.bross %in% get(paste0("fs.",col_name))]),
                  length(fs.hybrid[fs.hybrid %in% get(paste0("fs.",col_name))]),
                  length(fs.lasso[fs.lasso %in% get(paste0("fs.",col_name))]),
                  length(fs.elastic[fs.elastic %in% get(paste0("fs.",col_name))]),
                  length(fs.xgboost[fs.xgboost %in% get(paste0("fs.",col_name))]),
                  length(fs.GA[fs.GA %in% get(paste0("fs.",col_name))]),
                  length(fs.svm[fs.svm %in% get(paste0("fs.",col_name))]),
                  length(fs.boruta[fs.boruta %in% get(paste0("fs.",col_name))]),
                  length(fs.forward[fs.forward %in% get(paste0("fs.",col_name))]),
                  length(fs.backward[fs.backward %in% get(paste0("fs.",col_name))]),
                  length(fs.both[fs.both %in% get(paste0("fs.",col_name))]))
  fs.commonOneToOne[i] <- c(na, num_common[i:11])
}

```{r rf, warning=FALSE, cache=TRUE}
# Random Forest Feature Selection
start_time <- Sys.time()
rf_model <- randomForest(outcome ~ ., data = hdps.data, importance = TRUE)

@@

```{r rf2, warning=FALSE, cache=TRUE}
# Select features
fs_rf <- important_features_rf[important_features_rf %in% proxy.list]
proxy_rf <- paste0(fs_rf, collapse = "+")
form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
formula_rf <- as.formula(paste0("exposure", "~", form_rf))

@@

@@

@@

>>>>

**Method 1: Bross Formula**
```{r bross OR, warning=FALSE, cache=TRUE}
start_time <- Sys.time()

out3 <- get_prioritised_covariates(df = out2,
                                   patientIdVarname = "idx", 
                                   exposureVector = basetable$exposure,
                                   outcomeVector = basetable$outcome,
                                   patientIdVector = patientIds, 
                                   k = 100)
hdps.dim <- out3$autoselected_covariate_df

@@

```{r bross RD, warning=FALSE, cache=TRUE}
# Estimating RD and SE
hdps.dim.bross <- out3$autoselected_covariate_df
hdps.dim.bross$id <- hdps.dim.bross$idx
hdps.dim.bross$idx <- NULL
hdps.data.bross <- merge(data.complete[,c("id",
                                    outcome, 
                                    exposure, 
                                    investigator.specified.covariates)], 
                         hdps.dim.bross, 
                         by = "id")
hdps.data.bross$exposure <- as.numeric(I(hdps.data$obese=='Yes'))
hdps.data.bross$outcome <- as.numeric(I(hdps.data$diabetes=='Yes'))

proxyform <- paste0(fs.bross, collapse = "+")
covform <- paste0(investigator.specified.covariates, collapse = "+")
rhsformula <- paste0(c(covform, proxyform), collapse = "+")
ps.formula <- as.formula(paste0("exposure", "~", rhsformula))
out.formula <- as.formula(paste0("outcome","~", "exposure"))

W.out.bross <- weightit(ps.formula, 
                  data = hdps.data.bross, 
                  estimand = "ATE",
                  method = "ps")
fit_gau.bross <- glm(out.formula,
               data= hdps.data.bross,
               weights= W.out.bross$weights,
               family=gaussian(link= "identity"))

summary_rd.bross  <- summary(fit_gau.bross)$coef["exposure",
                                           c("Estimate",
                                             "Std. Error",
                                             "Pr(>|t|)")]
summary_rd.bross[2]<- sqrt(sandwich::sandwich(fit_gau.bross)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.bross, "exposure", level = 0.95,  method = "hc1")
summary_rd.bross  <- c(summary_rd.bross, conf.int)

round(summary_rd.bross, 2)
```

**Method 2: Hybrid Bross Formula & Lasso**
```{r hybrid OR, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()
proxy.list <- names(out3$autoselected_covariate_df[,-1])
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]
lasso.fit<-glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 1, 
                             nfolds = 5)
coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.hybrid <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.hybrid)
fs.hybrid <- proxy.list.sel.hybrid

@@

```{r hybrid RD, warning=FALSE, cache=TRUE}
proxyform <- paste0(fs.hybrid, collapse = "+")
covform <- paste0(investigator.specified.covariates, collapse = "+")
rhsformula <- paste0(c(covform, proxyform), collapse = "+")
ps.formula <- as.formula(paste0("exposure", "~", rhsformula))
out.formula <- as.formula(paste0("outcome","~", "exposure"))

W.out.hybrid <- weightit(ps.formula, 
                  data = hdps.data.bross, 
                  estimand = "ATE",
                  method = "ps")
fit_gau.hybrid <- glm(out.formula,
               data= hdps.data.bross,
               weights= W.out.hybrid$weights,
               family=gaussian(link= "identity"))

summary_rd.hybrid  <- summary(fit_gau.hybrid)$coef["exposure",
                                           c("Estimate",
                                             "Std. Error",
                                             "Pr(>|t|)")]
summary_rd.hybrid[2]<- sqrt(sandwich::sandwich(fit_gau.hybrid)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.hybrid, "exposure", level = 0.95,  method = "hc1")
summary_rd.hybrid  <- c(summary_rd.hybrid, conf.int)

round(summary_rd.hybrid, 2)
```

@@

proxy.list <- names(out2[,-1])    # length(proxy.list) :  142
covarsTfull <- c(investigator.specified.covariates, proxy.list)
Y.form <- as.formula(paste0(c("outcome~ exposure", 
                              covarsTfull), collapse = "+") )
```

**Method 3: Pure Lasso**
```{r lasso OR, warning=FALSE, cache=TRUE}
set.seed(42) # different seed -> different length for the selected proxy list
start_time <- Sys.time()
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]

lasso.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                               x = covar.mat, 
                               type.measure='mse',
                               family="binomial",
                               alpha = 1, 
                               nfolds = 5)

coef.fit<-coef(lasso.fit,s='lambda.min',exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.ml <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.ml)
fs.lasso <- proxy.list.sel.ml
proxy.lasso <- paste0(fs.lasso, collapse = "+")
form.lasso <- paste0(c(covform, proxy.lasso), collapse = "+")
formula.lasso <- as.formula(paste0("exposure", "~", form.lasso))

@@

```{r lasso RD, warning=FALSE, cache=TRUE}
fit_gau.lasso <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.lasso$weights,
                     family = gaussian(link= "identity"))

summary_rd.lasso  <- summary(fit_gau.lasso)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.lasso[2]<- sqrt(sandwich::sandwich(fit_gau.lasso)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.lasso, "exposure", level = 0.95,  method = "hc1")
summary_rd.lasso  <- c(summary_rd.lasso, conf.int)

round(summary_rd.lasso, 2)
```

**Method 4: Elastic Net**
```{r enet OR, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()
covar.mat <- model.matrix(Y.form, data = hdps.data)[,-1]

elas.fit <- glmnet::cv.glmnet(y = hdps.data$outcome, 
                             x = covar.mat, 
                             type.measure='mse',
                             family="binomial",
                             alpha = 0.5, 
                             nfolds = 5)

coef.fit<-coef(elas.fit, s='lambda.min', exact=TRUE)
sel.variables<-row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
proxy.list.sel.elastic <- proxy.list[proxy.list %in% sel.variables]
length(proxy.list.sel.elastic)
fs.elastic <- proxy.list.sel.elastic

@@

```{r enet RD, warning=FALSE, cache=TRUE}
fit_gau.elastic <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.elastic$weights,
                     family = gaussian(link= "identity"))

summary_rd.elastic  <- summary(fit_gau.elastic)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.elastic[2]<- sqrt(sandwich::sandwich(fit_gau.elastic)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.elastic, "exposure", level = 0.95,  method = "hc1")
summary_rd.elastic  <- c(summary_rd.elastic, conf.int)

round(summary_rd.elastic, 2)
```

**Method 5: XGBoost**
```{r xgb OR, warning=FALSE, cache=TRUE}
start_time <- Sys.time()

xgb_fit <- xgboost(data = covar.mat, label = hdps.data$outcome, 
                    max.depth = 20, eta = 1, nthread = 2, nrounds = 5, 
                    objective = "binary:logistic")

@@

```{r xgb RD, warning=FALSE, cache=TRUE}
fit_gau.xgboost <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.xgboost$weights,
                     family = gaussian(link= "identity"))

summary_rd.xgboost  <- summary(fit_gau.xgboost)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.xgboost[2]<- sqrt(sandwich::sandwich(fit_gau.xgboost)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.xgboost, "exposure", level = 0.95,  method = "hc1")
summary_rd.xgboost  <- c(summary_rd.xgboost, conf.int)

round(summary_rd.xgboost, 2)
```

@@

_GA (Genetic Algorithm) has no specific internal model building mechanism and would wrap around whatever model the user specifies_
```{r ga OR, warning=FALSE, cache=TRUE}
start_time <- Sys.time()

gaOpt <- function(vars, IV.train, DV.train) {
	varNames <- colnames(IV.train) #getting names of all variables
	selectedVarNames <- varNames[vars == "1"] # getting names of selected vars from GA
	gaSolutionData <- IV.train[,selectedVarNames] # keeping only those selected vars

@@

```{r ga RD, warning=FALSE, cache=TRUE}
fit_gau.GA <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.GA$weights,
                     family = gaussian(link= "identity"))

summary_rd.GA  <- summary(fit_gau.GA)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.GA[2]<- sqrt(sandwich::sandwich(fit_gau.GA)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.GA, "exposure", level = 0.95,  method = "hc1")
summary_rd.GA  <- c(summary_rd.GA, conf.int)

round(summary_rd.GA, 2)
```

@@

_(Long Running Time)_
```{r svm OR, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
svmTrainOutcome <- hdps.data$outcome
svmTrainOutcome[svmTrainOutcome == 0] <- -1
svmTrainPreds <- data.frame(covar.mat)

@@

```{r svm OR-cont, warning=FALSE, cache=TRUE}
fs.svm <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
fs.svm <- proxy.list[proxy.list %in% fs.svm]
proxy.svm <- paste0(fs.svm, collapse = "+")
form.svm <- paste0(c(covform, proxy.svm), collapse = "+")
formula.svm <- as.formula(paste0("exposure", "~", form.svm))

@@

```{r svm RD, warning=FALSE, cache=TRUE}
fit_gau.svm <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.svm$weights,
                     family = gaussian(link= "identity"))

summary_rd.svm  <- summary(fit_gau.svm)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.svm[2]<- sqrt(sandwich::sandwich(fit_gau.svm)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.svm, "exposure", level = 0.95,  method = "hc1")
summary_rd.svm  <- c(summary_rd.svm, conf.int)

round(summary_rd.svm, 2)
```

@@

_(Long Running Time)_
```{r Boruta OR, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()

boruta_output <- Boruta(Y.form, data = hdps.data, doTrace = 1)

sel.variables.bor <- names(boruta_output$finalDecision)[which(boruta_output$finalDecision != "Rejected")]
fs.boruta <- proxy.list[proxy.list %in% sel.variables.bor]
proxy.boruta <- paste0(fs.boruta, collapse = "+")
form.boruta <- paste0(c(covform, proxy.boruta), collapse = "+")
formula.boruta <- as.formula(paste0("exposure", "~", form.boruta))

@@

```{r Boruta RD, warning=FALSE, cache=TRUE}
fit_gau.boruta <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.boruta$weights,
                     family = gaussian(link= "identity"))

summary_rd.boruta  <- summary(fit_gau.boruta)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.boruta[2]<- sqrt(sandwich::sandwich(fit_gau.boruta)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.boruta, "exposure", level = 0.95,  method = "hc1")
summary_rd.boruta  <- c(summary_rd.boruta, conf.int)

round(summary_rd.boruta, 2)
```

**Method 9.1: Stepwise Regression (Forward)**
```{r fs OR, warning=FALSE, cache=TRUE}
set.seed(42)
start_time <- Sys.time()

initial_formula <- as.formula(paste0("outcome~exposure+",
                                     covform,
                                     collapse = "+"))
full_formula <- as.formula(paste0("outcome~exposure+",
                                  rhsformula,
                                  collapse = "+"))

@@

```{r fs RD, warning=FALSE, cache=TRUE}
fit_gau.forward <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.forward$weights,
                     family = gaussian(link= "identity"))

summary_rd.forward  <- summary(fit_gau.forward)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.forward[2]<- sqrt(sandwich::sandwich(fit_gau.forward)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.forward, "exposure", level = 0.95,  method = "hc1")
summary_rd.forward  <- c(summary_rd.forward, conf.int)

round(summary_rd.forward, 2)
```

**Method 9.2: Stepwise Regression (Backward)**
```{r bs OR, warning=FALSE, cache=TRUE}
start_time <- Sys.time()

stepwise_backward <- stepAIC(full_model, direction = "backward")

fs.backward <- all.vars(formula(stepwise_backward))[-1]
fs.backward <- proxy.list[proxy.list %in% fs.backward]
fs.backward <- fs.backward[fs.backward != "exposure"]
proxy.backward <- paste0(fs.backward, collapse = "+")
form.backward <- paste0(c(covform, proxy.backward), collapse = "+")
formula.backward <- as.formula(paste0("exposure", "~", form.backward))

@@

```{r bs RD, warning=FALSE, cache=TRUE}
fit_gau.backward <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.backward$weights,
                     family = gaussian(link= "identity"))

summary_rd.backward  <- summary(fit_gau.backward)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.backward[2]<- sqrt(sandwich::sandwich(fit_gau.backward)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.backward, "exposure", level = 0.95,  method = "hc1")
summary_rd.backward  <- c(summary_rd.backward, conf.int)

round(summary_rd.backward, 2)
```

**Method 9.3: Stepwise Regression (Both)**
```{r sw OR, warning=FALSE, cache=TRUE}
start_time <- Sys.time()

stepwise_both <- stepAIC(initial_model, 
                            scope = list(lower = initial_model, 
                                         upper = full_model), 
                            direction = "both")

fs.both <- all.vars(formula(stepwise_both))[-1]
fs.both <- proxy.list[proxy.list %in% fs.both]
proxy.both <- paste0(fs.both, collapse = "+")
form.both <- paste0(c(covform, proxy.both), collapse = "+")
formula.both <- as.formula(paste0("exposure", "~", form.both))

@@

```{r sw RD, warning=FALSE, cache=TRUE}
fit_gau.both <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out.both$weights,
                     family = gaussian(link= "identity"))

summary_rd.both  <- summary(fit_gau.both)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.both[2]<- sqrt(sandwich::sandwich(fit_gau.both)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.both, "exposure", level = 0.95,  method = "hc1")
summary_rd.both  <- c(summary_rd.both, conf.int)

round(summary_rd.both, 2)
```

```{r rf OR, warning=FALSE, cache=TRUE}
# Random Forest Feature Selection
start_time <- Sys.time()

rf_model <- randomForest(outcome ~ ., data = hdps.data, importance = TRUE)

@@

```{r rf OR-cont, warning=FALSE, cache=TRUE}
# Select features
fs_rf <- important_features_rf[important_features_rf %in% proxy.list][1:100]
proxy_rf <- paste0(fs_rf, collapse = "+")
form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
formula_rf <- as.formula(paste0("exposure", "~", form_rf))

@@

```{r rf RD, warning=FALSE, cache=TRUE}
fit_gau.rf <- glm(out.formula,
                     data = hdps.data,
                     weights = W.out_rf$weights,
                     family = gaussian(link= "identity"))

summary_rd.rf  <- summary(fit_gau.rf)$coef["exposure",
                                                 c("Estimate",
                                                   "Std. Error",
                                                   "Pr(>|t|)")]
summary_rd.rf[2]<- sqrt(sandwich::sandwich(fit_gau.rf)[2,2])

require(lmtest)
conf.int <- confint(fit_gau.rf, "exposure", level = 0.95,  method = "hc1")
summary_rd.rf  <- c(summary_rd.rf, conf.int)

round(summary_rd.rf, 2)
```

Naming consistence:
```{r}
sum_ci.rf <- sum_ci_rf
fs.rf <- fs_rf
```

Comparing the Results:
```{r compare, warning=FALSE, cache=TRUE}
sum_ci.all <- rbind(sum_ci.bross, sum_ci.lasso, sum_ci.hybrid, sum_ci.elastic, 
                    sum_ci.svm, sum_ci.GA, 
                    sum_ci.xgboost, sum_ci.rf, sum_ci.boruta,
                    sum_ci.forward, sum_ci.backward, sum_ci.both)

OR.data <- data.frame(method = c("bross", "lasso", "hybrid", "elastic", 
                                 "SVM", "GA",
                                 "xgboost", "rf", "boruta", 
                                 "forward", "backward", "both"),
                      OR = exp(sum_ci.all[,2]),
                      lower = exp(sum_ci.all[,5]),
                      upper = exp(sum_ci.all[,6]))

OR.data$method <- factor(OR.data$method, 
                         levels = c("both", "backward", "forward",
                                    "boruta", "rf", "xgboost", 
                                    "GA", "SVM", 
                                    "elastic", "hybrid", "lasso", "bross"))

fs.all <- data.frame(numFeature = c(length(fs.bross), 
                                    length(fs.lasso),
                                    length(fs.hybrid),
                                    length(fs.elastic), 
                                    length(fs.svm),
                                    length(fs.GA),
                                    length(fs.xgboost),
                                    length(fs.rf),
                                    length(fs.boruta),
                                    length(fs.forward),
                                    length(fs.backward),
                                    length(fs.both)),
                     numInCommon = c(NA,
                                     length(fs.lasso[fs.lasso %in% fs.bross]),
                                     length(fs.hybrid[fs.hybrid %in% fs.bross]),
                                     length(fs.elastic[fs.elastic %in% fs.bross]),
                                     length(fs.svm[fs.svm %in% fs.bross]),
                                     length(fs.GA[fs.GA %in% fs.bross]),
                                     length(fs.xgboost[fs.xgboost %in% fs.bross]),
                                     length(fs.rf[fs.rf %in% fs.bross]),
                                     length(fs.boruta[fs.boruta %in% fs.bross]),
                                     length(fs.forward[fs.forward %in% fs.bross]),
                                     length(fs.backward[fs.backward %in% fs.bross]),
                                     length(fs.both[fs.both %in% fs.bross])))
rownames(fs.all) <-  c("bross", "lasso", "hybrid", "elastic", 
                       "SVM", "GA",
                       "xgboost", "rf", "boruta", 
                       "forward", "backward", "both")

fs.commonOneToOne <- data.frame(ini = rep(NA, 12))

for (i in 1:12) {
  col_name <- OR.data$method[i]
  if (col_name == "SVM") {
    col_name <- "svm"
  }
  na.i <- 1
  na <- c()
  while (na.i < i) {
    na <- c(na, NA)
    na.i <- na.i + 1
  }
  num_common <- c(length(fs.bross[fs.bross %in% get(paste0("fs.",col_name))]),
                  length(fs.lasso[fs.lasso %in% get(paste0("fs.",col_name))]),
                  length(fs.hybrid[fs.hybrid %in% get(paste0("fs.",col_name))]),
                  length(fs.elastic[fs.elastic %in% get(paste0("fs.",col_name))]),
                  length(fs.svm[fs.svm %in% get(paste0("fs.",col_name))]),
                  length(fs.GA[fs.GA %in% get(paste0("fs.",col_name))]),
                  length(fs.xgboost[fs.xgboost %in% get(paste0("fs.",col_name))]),
                  length(fs.rf[fs.rf %in% get(paste0("fs.",col_name))]),
                  length(fs.boruta[fs.boruta %in% get(paste0("fs.",col_name))]),
                  length(fs.forward[fs.forward %in% get(paste0("fs.",col_name))]),
                  length(fs.backward[fs.backward %in% get(paste0("fs.",col_name))]),
                  length(fs.both[fs.both %in% get(paste0("fs.",col_name))]))
  fs.commonOneToOne[i] <- c(na, num_common[i:12])
}

@@

```{r}
important_features_rfe
```

Why does this codechunk not work?
No proxy is selected by rfe. it only selects diabetes.
ERROR: the formula in wrong format (ending with "+")
" e ~ a+b+c+ "

@@

```{r save}
# Save the entire workspace to a file named "workspace.RData"
save.image(file = "data/workspace.RData")
```

```{r OR.ci_plot with # of proxy}

OR.ci_plot_new <- ggplot(OR.data, aes(y = method, x = OR)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) + 
  geom_text(aes(label = fs.all[,1], x = OR, y = method),
            vjust = -0.8,  # Adjust vertical position
            hjust = -1, # Adjust horizontal position
            size = 3, 
            color = "dark green") +
  labs(title = "Odds Ratios with 95% Confidence Intervals",
       x = "Odds Ratio",
       y = "Method")
```

RD comparison:
```{r summary RD all methods}
sum.rd_all <- rbind(summary_rd.bross,
                    summary_rd.hybrid,
                    summary_rd.lasso,
                    summary_rd.elastic,
                    summary_rd.svm,
                    summary_rd.GA,
                    summary_rd.xgboost,
                    summary_rd.rf,
                    summary_rd.boruta,
                    summary_rd.forward,
                    summary_rd.backward,
                    summary_rd.both)

rownames(sum.rd_all) <- c("bross", "hybrid", "lasso", "elastic", 
                          "SVM", "GA",
                          "xgboost", "rf", "boruta", 
                          "forward", "backward", "both")
```

```{r save RD}
# Save the entire workspace to a file named "workspaceNew.RData"
save.image(file = "data/workspaceNew.RData")
```

```{r print RD result table}
round(sum.rd_all, 3)
```

```{r print OR.ci_plot with # of proxy}
OR.ci_plot_new
```
